\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-29 paper/main.tex

\subsection{Baseline model}
Our aim is to develop and evaluate a computational model to predict
drug--target interactions. Specifically, given a protein, we are
interested in identifying the drugs that may target the protein; this
scenario is motivated by the need to identify drugs that can target a
specific protein that may be associated with a disease or abnormal
phenotypes.
Our aim is further to combine two different types of features:
structural information based on protein structure and molecular drug composition, and their respective observable characteristics. \\

@@

>>>>

\subsection{Baseline model}
Our aim is to develop and evaluate a computational model to predict
drug--target interactions. Specifically, given a protein, we are
interested in identifying the drugs that may target the protein; this
scenario is motivated by the need to identify drugs that can target a

\subsection{\name identifies drugs that target a protein}

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two 
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and

This scenario is motivated by the need to identify drugs that can target a
specific protein that may be associated with a disease or abnormal
phenotypes.
Our aim is further to combine two different types of features:
structural information based on protein structure and molecular drug composition, and their respective observable characteristics. \\

@@

To obtain a prediction for a given drug-protein pair\todo{should this
  be about pairs, or rather something like ``given a protein, we aim
  to find a drug...''? I.e., find a consistent way to separate
  yourself language-wise from a naive prediction of pairs.}, we first
build DL2vec representations\todo{In results: talk about what they are
supposed to DO (``embeddings/representations of the phenotypes and
functions...''), not how you implement them (you could use something
else, for example).} for both drugs and proteins over PhenomeNET, while also preparing structural, molecular representations. Hence, we pretrain the siamese networks for both molecular and ontology features, yielding the deep neural network transformers for both methods and both drugs and proteins, individually. These embeddings are now added to the graph neural network as node features, where we start an end-to-end learning and training process. Notably, like in the pretraining phase, we rely on siamese neural networks, enforcing similar representations for fitting drug-protein pairs. The overall architecture can be seen in Figure~\ref{fig:Fullmodel}.
